Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-13 _paper.rmd
-Clarify PCP distribution - manual screen shots/annotation

<!-- Tour start frame -->
The initial frame is the normalized SHAP values of the PI. The current projection basis is depicted as the width of a bar, the feature's contribution to the horizontal axis. The normalized values of all instances are shown as vertical parallel coordinate plots.

@@

```{r classificationcase, echo=F, out.width = "100%", fig.align="center", fig.cap = "Overview of the cheem viewer for classification tasks. Plots are colored on predicted class, and red circles indicate misclassified instances. Model visual is essentially a representation of the confusion matrix of the model. The radial tour is a 1D projection starting the attribution projection. The first frame is the linear feature importances that best describe the instance's prediction. We probe the support of feature contributions by selecting a feature and use the radial tour to vary its coefficient."}
knitr::include_graphics("./figures/app_classification.PNG")
```

>>>>

<!-- Tour start frame -->
The initial frame is the normalized SHAP values of the PI. The distribution normalized values from all instances are shown depicted in the basis as vertical parallel coordinate plots, where each line connects an instance's feature attribution. The PI is highlighted as larger dashed line and CI as  a dotted line. The current projection basis is depicted as the width of a bar, the feature contributions to the horizontal axis.

@@

```{r classificationcase, echo=F, out.width = "100%", fig.align="center", fig.cap = "Overview of the cheem viewer for classification tasks. Plots are colored on predicted class, and red circles indicate misclassified instances. Model visual is essentially a representation of the confusion matrix of the model. The radial tour is a 1D projection starting the attribution projection. The first frame is the linear feature importances that best describe the instance's prediction. We probe the support of feature contributions by selecting a feature and use the radial tour to vary its coefficient."}
knitr::include_graphics("./figures/app_classification_annotations.PNG")
```
